### 2021-07-05 rad-icfp-2021/relwork.tex
minor

\subsection{Summary} % (fold)
\label{sub:summary}

We have introduced a transformation on programs to compute provably efficient (\ref{sec:complexity}) 
gradients via reverse derivatives in a purely functional way (\ref{sub:Macro for pure reverse mode transformation})
on a simple yet expressive language with functions on arrays (\ref{sub:sourcelang}), 
combined with standard functional optimizations (\ref{fig:optim}).  
We introduced a novel intermediate representation, unary form (\ref{sec:unf}) 
to decompose our transformation into simpler transformations.
We gave denotational semantics to our languages and our transformations (\ref{sec:correctness}) 
and showed correctness of the reverse-mode transformation (\ref{sub:Correctness theorem}).
We showed (\ref{sec:generalization}) how to lift some of the restrictions that
we introduced on arrays and how to extend our approach to a richer language with more primitive operations and conditionals.

\subsection{Related Work} % (fold)
\label{sub:related_work}

@@

\subsection{Discussion and future work} % (fold)
\label{sub:discussion_and_future_work}

\noindent \textbf{implementation, BLaS, benchmark}

\noindent \textbf{Higher-order functions}
Matthijs'work, use of defunctionalization, question efficiency and usefulness, 
interested in functions like root of function or minimal of a function. Implicit function theorem

\MH{should talk a bit about the recent paper: reverse AD in Dex \cite{paszke2021getting}}
\clearpage

>>>>

\section{Discussion and future work} % (fold)
\label{sec:discussion_and_future_work}

% \noindent \textbf{implementation, BLaS, benchmark}

\noindent \textbf{Higher-order functions}
Matthijs'work, use of defunctionalization, question efficiency and usefulness, 
interested in functions like root of function or minimal of a function. Implicit function theorem
Some recent work \cite{vakar2020reverse,sherman2021} present reverse-mode in a higher-order language.
\cite{vakar2020reverse} uses categorical semantics to show correctness of the reverse-mode transformation 
and \cite{sherman2021} uses sophisticated higher-order primitives such as root finding, max, argmax or integral. 
Their work focuses on computable reals which is hard to compare in terms of efficiency 
with our more standard approach of AD.

\MH{should talk a bit about the recent paper: reverse AD in Dex \cite{paszke2021getting}}

\section{Related Work} % (fold)
\label{sec:related_work}

@@

We have introduced a transformation on programs to compute provably efficient (\ref{sec:complexity}) 
gradients via reverse derivatives in a purely functional way (\ref{sub:Macro for pure reverse mode transformation})
on a simple yet expressive language with functions on arrays (\ref{sub:sourcelang}), 
combined with standard functional optimizations (\ref{fig:optim}).  
We introduced a novel intermediate representation, unary form (\ref{sec:unf}) 
to decompose our transformation into simpler transformations.
We gave denotational semantics to our languages and our transformations (\ref{sec:correctness}) 
and showed correctness of the reverse-mode transformation (\ref{sub:Correctness theorem}).
We showed (\ref{sec:generalization}) how to lift some of the restrictions that
we introduced on arrays and how to extend our approach to a richer language with more primitive operations and conditionals.
\clearpage
